---
title: "Final_Network"
author: "Courtney C"
date: "2026-02-03"
output: html_document
---

```{r}
library(ggpubr)
library(ggraph)
library(dplyr)
library(igraph) 
library(sna)
library(intergraph)
library(gplots)
```


```{r}
data <- read.csv("COCAINE_DEALING.csv")
```

```{r}
adj_matrix <- as.matrix(data)
```

```{r}
library(igraph)

raw_data <- read.csv("COCAINE_DEALING.csv", check.names = FALSE)


row_names <- raw_data[, 1]

adj_matrix <- as.matrix(raw_data[, -1])

rownames(adj_matrix) <- row_names

dim(adj_matrix)
nrow(adj_matrix) == ncol(adj_matrix)


```
```{r}
net <- graph_from_adjacency_matrix(
  adj_matrix,
  mode = "directed",
  weighted = TRUE,
  diag = TRUE
)

net
```

```{r}
un_net <- graph_from_adjacency_matrix(
  adj_matrix,
  mode = "undirected",
  weighted = TRUE,
  diag = FALSE
)

net
un_net
```


```{r}
ggraph(net, layout = "kk") + 
  geom_edge_link() + 
  geom_node_point() +
  ggnetwork::theme_blank()
```

```{r}
ggraph(net, layout = "stress") + 
  geom_edge_link() + 
  geom_node_point() +
  ggnetwork::theme_blank()
```

```{r}
ggraph(net, layout = "stress") +
  geom_edge_link() +
  geom_node_point(
    aes(color = ifelse(name == "Kay", "highlight", "normal")),
    size = ifelse(V(net)$name == "Kay", 5, 2)
  ) +
  geom_node_label(
    aes(label = ifelse(name == "Kay", name, ""),
        color = ifelse(name == "Kay", "highlight", "normal")),
    repel = TRUE, 
    size = 5,
    fontface = "bold",
    fill = "lightyellow",
    label.size = 0.5
  ) +
  scale_color_manual(values = c("highlight" = "skyblue", "normal" = "black"), guide = "none") +
  ggnetwork::theme_blank()
```

```{r}
ggraph(net, layout = "stress") +
  geom_edge_link(arrow = grid::arrow(angle = 20, #how wide should the arrow be
                                      length = unit(0.10, "in"), #how long should the arrow be
                                      type = "closed")) + #vs open arrow
  geom_node_point() +
  ggnetwork::theme_blank()

ggraph(net, layout = "stress") +
  geom_edge_link(aes(width = weight)) + #weight is the name of the variable for tie strength
  scale_edge_width(range = c(0.15, 2)) + #default width is VERY wide, so I recommend reducing
  geom_node_point() +
  ggnetwork::theme_blank() + 
  theme(legend.position = "none") # I don't find the legend necessary in this case

ggraph(net, layout = "stress") + 
  geom_edge_link0(edge_color=ifelse(E(net)$friends == 1, "#82260d", "grey50")) + #friendly ties are red, others are grey
  #NOTE to get colors to render you must use geom_edge_link0 rather than geom_edge_link
  geom_node_point() +
  ggnetwork::theme_blank()
```


```{r}
# Check what vertex/edge attributes we have
print(net)
cat("\nVertex attributes:", vertex_attr_names(net), "\n")
cat("Edge attributes:", edge_attr_names(net), "\n")
```



```{r}
library(ggraph)
library(igraph)

ggraph(net, layout = "fr") +
  geom_edge_link(aes(alpha = 0.5), arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(3, 'mm')) +
  geom_node_point(aes(size = ifelse(name == "kay", 4, 2),
                      color = ifelse(name == "kay", "Kay", "Other")),
                  show.legend = FALSE) +
  geom_node_text(aes(label = ifelse(name == "kay", "KAY", NA)),
                 color = "red", fontface = "bold", size = 6,
                 repel = TRUE, nudge_y = 0.2) +
  scale_color_manual(values = c("Kay" = "gold", "Other" = "lightblue")) +
  scale_size_manual(values = c(4, 2)) +
  theme_void() +
  labs(title = "Communication Network - Kay Highlighted")
```

```{r}
igraph::vcount(net)
igraph::ecount(net)
```

```{r}
#### degree####
deg <- igraph::degree(net) #total degree
deg 
deg_u <- igraph::degree(un_net) #total degree
deg_u
# directed and undirected are the same, because it's the total number of ties found in the edgelist

ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(
    aes(fill = ifelse(name == "Kay", "highlight", "normal"),
        size = igraph::degree(net, mode = "all")),
    color = "black", 
    shape = 21
  ) +
  scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  guides(fill = "none") +  # Additional explicit removal
  ggnetwork::theme_blank()
```


```{r}
# in degree####
deg_in <- igraph::degree(net, mode = "in") #in degree
deg_in
deg_in_u <- igraph::degree(un_net, mode = "in") #in degree
deg_in_u
#directed and undirected are NOT the same, because now we are accounting for tie direction in the calculation

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5,
                 arrow = grid::arrow(angle = 20,
                                     length = unit(0.10, "in"),
                                     type = "closed"),
                 start_cap = circle(2, 'mm'),  # Reduced from 10 to 2
                 end_cap = circle(2, 'mm')) +  # Reduced from 10 to 2
                 
  geom_node_point(
    aes(fill = ifelse(name == "Kay", "highlight", "normal"),
        size = igraph::degree(net, mode = "in")),
    color = "black", 
    shape = 21
  ) +
  scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  guides(size = "none") +  # This removes the size legend
  ggnetwork::theme_blank()
```
```{r}
# out degree####
deg_out <- igraph::degree(net, mode = "out") #out degree
deg_out
deg_out_u <- igraph::degree(un_net, mode = "out") #out degree
deg_out_u
#directed and undirected are NOT the same, because now we are accounting for tie direction in the calculation

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5,
                 arrow = grid::arrow(angle = 20,
                                     length = unit(0.10, "in"),
                                     type = "closed"),
                 start_cap = circle(2, 'mm'),  # Reduced from 10 to 2
                 end_cap = circle(2, 'mm')) +  # Reduced from 10 to 2
                 
  geom_node_point(
    aes(fill = ifelse(name == "Kay", "highlight", "normal"),
        size = igraph::degree(net, mode = "out")),
    color = "black", 
    shape = 21
  ) +
  scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  guides(size = "none") +  # This removes the size legend
  ggnetwork::theme_blank()
```

```{r}
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = V(net)$deg <- igraph::degree(net, mode = "all")) + #node size is now based on degree rather than a number of your choosing
      scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  ggnetwork::theme_blank()


```


```{r}
#### closeness####
close <- igraph::closeness(net) #closeness
close #careful with this - isolates can be tricky
summary(close)

# More info: https://igraph.org/r/doc/closeness.html#:~:text=If%20no%20other%20vertices%20are,calculates%20the%20exact%20closeness%20scores.
# If there is no (directed) path between vertex v and i, then i is omitted from the calculation. 
# If no other vertices are reachable from v, then its closeness is returned as NaN

ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5, 
                  arrow = grid::arrow(angle = 20,
                                      length = unit(0.10, "in"),
                                      type = "closed")) +#, 
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = igraph::closeness(net)*15) +
  ggnetwork::theme_blank()

un_close <- igraph::closeness(un_net) #closeness
un_close
summary(un_close) #now there is no missingness

ggraph(un_net) + 
  geom_edge_link0(color = "black", alpha = .5) + 
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = igraph::closeness(un_net)*200) + # mess with number here becuase number is so small!
  ggnetwork::theme_blank(legend.position = "none")
```

```{r}
# in closeness####
close_in <- igraph::closeness(net, mode = "in") #closeness
close_in #careful with this - isolates can be tricky
summary(close_in)

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  arrow = grid::arrow(angle = 20,
                                      length = unit(0.10, "in"),
                                      type = "closed")) + 
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21,
                  size = igraph::closeness(net, mode = "in")*10) +
  ggnetwork::theme_blank()
```


```{r}
#### betweenness####
bet_d <- igraph::betweenness(net)
summary(bet_d)

bet_dF <- igraph::betweenness(net, directed = F)
summary(bet_dF)
#OR
bet_u <- igraph::betweenness(un_net)
summary(bet_u)

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  arrow = grid::arrow(angle = 20,
                                      length = unit(0.10, "in"),
                                      type = "closed")) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21,
                  size = igraph::betweenness(net)/25) +
  ggnetwork::theme_blank()

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5) + 
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21,
                  size = igraph::betweenness(net, directed = F)/50) +
  ggnetwork::theme_blank()

ggraph(un_net) + 
  geom_edge_link(color = "black", alpha = .5) + 
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21,
                  size = igraph::betweenness(un_net)/50) +
  ggnetwork::theme_blank()
```

```{r}
# edge betweenness####
eb_d <- edge_betweenness(net, directed = T)
summary(eb_d)

eb_dF <- edge_betweenness(net, directed = F)
summary(eb_dF)
#OR
eb_u <- edge_betweenness(un_net)
summary(eb_u)

ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  arrow = grid::arrow(angle = 20,
                                      length = unit(0.10, "in"),
                                      type = "closed"),
                  aes(width = edge_betweenness(net, directed = T))) +
  scale_edge_width(range = c(0.15, 2)) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21) + 
  ggnetwork::theme_blank(legend.position = "none") 

ggraph(un_net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  aes(width = edge_betweenness(net, directed = F))) +
  scale_edge_width(range = c(0.15, 2)) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21) + 
  ggnetwork::theme_blank(legend.position = "none") 

```
```{r}
# edge betweenness####
eb_d <- edge_betweenness(net, directed = T)
summary(eb_d)

eb_dF <- edge_betweenness(net, directed = F)
summary(eb_dF)
#OR
eb_u <- edge_betweenness(un_net)
summary(eb_u)

# Directed network with Kay highlighted
ggraph(net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  arrow = grid::arrow(angle = 20,
                                      length = unit(0.10, "in"),
                                      type = "closed"),
                  aes(width = edge_betweenness(net, directed = T))) +
  scale_edge_width(range = c(0.15, 2)) +
  geom_node_point(
    aes(fill = ifelse(name == "Kay", "highlight", "normal")),
    color = "black", 
    shape = 21,
    size = 3  # Added fixed size (adjust as needed)
  ) + 
  scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  ggnetwork::theme_blank(legend.position = "none") 

# Undirected network with Kay highlighted
ggraph(un_net) + 
  geom_edge_link(color = "black", alpha = .5, 
                  aes(width = edge_betweenness(un_net, directed = F))) +
  scale_edge_width(range = c(0.15, 2)) +
  geom_node_point(
    aes(fill = ifelse(name == "Kay", "highlight", "normal")),
    color = "black", 
    shape = 21,
    size = 3  # Added fixed size (adjust as needed)
  ) + 
  scale_fill_manual(
    values = c("highlight" = "skyblue", "normal" = "#EFD9D3"),
    guide = "none"
  ) +
  ggnetwork::theme_blank(legend.position = "none")
```


```{r}
#### eigenvector centrality####
evc_undir <- eigen_centrality(net, directed = F)$vector #must pull the vector
summary(evc_undir)
#OR
evc_undir <- eigen_centrality(un_net)$vector
summary(evc_undir)

ggraph(un_net) + 
  geom_edge_link(color = "black", alpha = .5) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = igraph::eigen_centrality(un_net)$vector*10) +
  ggnetwork::theme_blank()
```
```{r}
# Calculate eigenvector centrality
eigen_d <- eigen_centrality(net, directed = TRUE)$vector
eigen_u <- eigen_centrality(un_net, directed = FALSE)$vector

# See the values
eigen_d
summary(eigen_d)

# Visualize (nodes with high eigenvector centrality are larger/darker)
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .3) +
  geom_node_point(
    aes(size = eigen_centrality(net)$vector,
        fill = eigen_centrality(net)$vector),
    shape = 21,
    color = "black"
  ) +
  scale_size_continuous(range = c(2, 10)) +
  scale_fill_gradient(low = "#EFD9D3", high = "#82260d") +
  ggnetwork::theme_blank() +
  theme(legend.position = "right")
```


```{r}
#### graph strength####
gs <- strength(net, mode = "all")
summary(gs)
# sum of the weights of edges connected to the node (can also calculate manually)

ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#EFD9D3", color = "black",
                  shape = 21, 
                  size = strength(net, mode = "all")/5) +
  ggnetwork::theme_blank()
```

```{r}
# in####
gs_in <- strength(net, mode = "in")
gs_in

# Create a logical vector for Kay
is_kay <- V(net)$name == "Kay"

ggraph(net) +
  geom_edge_link(color = "black", alpha = .5,
                 arrow = grid::arrow(angle = 20,
                                     length = unit(0.15, "in"),
                                     type = "closed"),
                 start_cap = circle(2, 'mm'),
                 end_cap = circle(2, 'mm')) +
  geom_node_point(aes(fill = ifelse(is_kay, "kay", "normal"),
                      size = strength(net, mode = "in")/3),
                  color = "black",
                  shape = 21) +
  scale_fill_manual(values = c("kay" = "skyblue", "normal" = "#EFD9D3"),
                    guide = "none") +
  scale_size_identity() +  # Preserves the exact sizes from strength/2
  ggnetwork::theme_blank()
```


```{r}
# in####
gs_in <- strength(net, mode = "in")
gs_in

ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#EFD9D3", color = "black",
                  shape = 21, 
                  size = strength(net, mode = "in")/2) +
  ggnetwork::theme_blank()
```

```{r}
# out####
gs_out <- strength(net, mode = "out")
gs_out

ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#EFD9D3", color = "black",
                  shape = 21, 
                  size = strength(net, mode = "out")/2) +
  ggnetwork::theme_blank()
```
```{r}
# out####
gs_out <- strength(net, mode = "out")
gs_out

# Create a logical vector for Kay
is_kay <- V(net)$name == "Kay"

ggraph(net) +
  geom_edge_link(color = "black", alpha = .5,
                 arrow = grid::arrow(angle = 20,
                                     length = unit(0.15, "in"),
                                     type = "closed"),
                 start_cap = circle(2, 'mm'),
                 end_cap = circle(2, 'mm')) +
  geom_node_point(aes(fill = ifelse(is_kay, "kay", "normal"),
                      size = strength(net, mode = "out")/3),
                  color = "black",
                  shape = 21) +
  scale_fill_manual(values = c("kay" = "skyblue", "normal" = "#EFD9D3"),
                    guide = "none") +
  scale_size_identity() +  # Preserves the exact sizes from strength/2
  ggnetwork::theme_blank()
```
```{r}
gs_out <- strength(net, mode = "out")
gs_out

# Create a logical vector for Kay
is_kay <- V(net)$name == "Kay"

ggraph(net) +
  geom_edge_link(color = "black", alpha = .5,
                 arrow = grid::arrow(angle = 20,
                                     length = unit(0.15, "in"),
                                     type = "closed"),
                 start_cap = circle(2, 'mm'),
                 end_cap = circle(2, 'mm')) +
  geom_node_point(aes(fill = ifelse(is_kay, "kay", "normal"),
                      size = strength(net, mode = "out")/3),
                  color = "black",
                  shape = 21) +
  scale_fill_manual(values = c("kay" = "skyblue", "normal" = "#EFD9D3"),
                    guide = "none") +
  scale_size_identity() +
  expand_limits(y = c(NA, 5.)) +  # Expands only the top (max y) to 2
  ggnetwork::theme_blank()
```


```{r}
#### whole network centrality####
## centralization####
# max####
star_graph <- make_star(100, mode = "undirected")

ggraph(star_graph, layout = "star") + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#DFE6EB", 
                  color = "black", 
                  size = 10, 
                  shape = 21) +
  ggnetwork::theme_blank() 

cent_deg_star <- centr_degree(star_graph, mode = "all")$centralization
round(cent_deg_star, digits = 2)
cent_clo_star <- centr_clo(star_graph, mode = "all")$centralization
round(cent_clo_star, digits = 2)
cent_bet_star <- centr_betw(star_graph)$centralization
round(cent_bet_star, digits = 2)

g_mt <- make_empty_graph(100)
g_mt <- add_edges(g_mt, c(1, 2))
ggraph(g_mt, layout = "tree") + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(fill = "#DFE6EB", color = "black", size = 10, shape = 21) +
  ggnetwork::theme_blank() 

cent_evc_iso <- centr_eigen(g_mt)$centralization
round(cent_evc_iso, digits = 2)
```

```{r}
# degree centralization####
cent_deg <- centr_degree(net, mode = "all")$centralization
round(cent_deg, digits = 2)
```

```{r}
# closeness centralization####
cent_clo <- centr_clo(net, mode = "all")$centralization
round(cent_clo, digits = 2)
```

```{r}
# betweenness centralization####
cent_bet <- centr_betw(net)$centralization
round(cent_bet, digits = 2)
```

```{r}
# eigenvector centralization####
cent_evc <- centr_eigen(net)$centralization
round(cent_evc, digits = 2)
```

```{r}
edges <- as.data.frame(as_edgelist(net))
names(edges) <- c("from", "to") 
edges$weight <- E(net)$weight  

nodes <- data.frame(name = V(net)$name)

net <- graph_from_data_frame(edges, directed = T, vertices = nodes)

net
is_simple(net)
net_s <- igraph::simplify(net)
is_simple(net_s)
net_s_sna <- asNetwork(net_s) #converts igraph to sna object

un_net <- graph_from_data_frame(edges, directed = F, vertices = nodes)
un_net

net_sna <- network(edges, matrix.type = "edgelist", directed = T) #  ...
net_sna

un_net_sna <- network(edges, matrix.type = "edgelist", directed = F, multiple = T, vertex.attr = nodes) 
un_net_sna  

edges$mult <- which_multiple(un_net)
edges2 <- edges %>% filter(mult != TRUE)
un_net_sna <- network(edges2, matrix.type = "edgelist", directed = F, vertex.attr = nodes)
```

```{r}
#### Dyads####
igraph::dyad_census(net)
sna::dyad.census(net_sna)

sna::mutuality(net_sna)
igraph::reciprocity(net) # what % are mutual?
igraph::which_mutual(net)
```
```{r}
#### Directed Triad Census####
# Triad types (cite: Davis & Leinhardt):
  # 003  A, B, C (empty)
  # 012  A->B, C
  # 102  A<->B, C
  # 021D A<-B->C
  # 021U A->B<-C
  # 021C A->B->C
  # 111D A<->B<-C
  # 111U A<->B->C
  # 030T A->B<-C, A->C
  # 030C A<-B<-C, A->C
  # 201  A<->B<->C 
  # 120D A<-B->C, A<->C
  # 120U A->B<-C, A<->C
  # 120C A->B->C, A<->C
  # 210  A->B<->C, A<->C
  # 300  A<->B<->C, A<->C (complete)

igraph::triad_census(net)
sna::triad.census(net_sna) #preferred because it has clear labels
colnames(sna::triad.census(net_sna))[which.max(sna::triad.census(net_sna))] #which triad is the most common?
colnames(sna::triad.census(net_sna))[which.min(sna::triad.census(net_sna))]
```
```{r}
#### Transitivity####
# local####
trans <- igraph::transitivity(net, type = "local", isolates = "zero") # you can pick 0 or missing for isolates
# can say that isolates are NaN or zero
summary(trans)
```

```{r}
# global####
trans <- igraph::transitivity(net, type = "global")
trans

sna::gtrans(net_sna) 
# the sna package version of transitivity doesn't have an argument for local, so only used for global

# Weak and Weak Census
  # weak: a->b-> => a->c
  # weak census: num transitive triads
  # transitive triads are those where a -> b, b -> c, and a -> c
gtrans(net_sna, mode='digraph', measure='weak')

# Strong and Strong Census
  # strong: a->b-> <=> a->c
  # strong census: num all triads
gtrans(net_sna, mode='digraph', measure='strong')
```

```{r}
# constraint####
# constraint is higher is ego has more redundant ties
igraph::constraint(net)
summary(igraph::constraint(net))
```

```{r}
# efficiency####
global_efficiency(net)
# Global efficiency is the average of the inverse distances between all pairs of nodes 
# 0 if pair isn't reachable 

local_efficiency(net)
# To calcuate local efficienty, remove node and compute the shortest paths between neighbors
# Take the average of the inverse of the shortest path distances.
# 0 if node has fewer than two ties or isn't reachable

average_local_efficiency(net)
# Average local efficiency is the mean of the local efficiencies
```

```{r}
#### density####
den <- igraph::edge_density(net) 
den

sna::gden(net_sna, mode = 'digraph') #digraph is directed graph, graph is undirected graph
```


```{r}
# global####
trans <- igraph::transitivity(net, type = "global")
trans

sna::gtrans(net_sna) 
# the sna package version of transitivity doesn't have an argument for local, so only used for global

# Weak and Weak Census
  # weak: a->b-> => a->c
  # weak census: num transitive triads
  # transitive triads are those where a -> b, b -> c, and a -> c
gtrans(net_sna, mode='digraph', measure='weak')

# Strong and Strong Census
  # strong: a->b-> <=> a->c
  # strong census: num all triads
gtrans(net_sna, mode='digraph', measure='strong')
```


```{r}
# constraint####
# constraint is higher is ego has more redundant ties
igraph::constraint(net)
summary(igraph::constraint(net))
```

```{r}
# efficiency####
global_efficiency(net)
# Global efficiency is the average of the inverse distances between all pairs of nodes 
# 0 if pair isn't reachable 

local_efficiency(net)
# To calcuate local efficienty, remove node and compute the shortest paths between neighbors
# Take the average of the inverse of the shortest path distances.
# 0 if node has fewer than two ties or isn't reachable

average_local_efficiency(net)
# Average local efficiency is the mean of the local efficiencies
```

```{r}
#### density####
den <- igraph::edge_density(net) 
den

sna::gden(net_sna, mode = 'digraph') #digraph is directed graph, graph is undirected graph
```

```{r}
#### assortativity####

    
```

```{r}
## diameter####
igraph::diameter(net) #longest geodesic
igraph::diameter(net, directed = F) #longest geodesic for undirected graph
igraph::diameter(un_net) #longest geodesic for undirected graph

igraph::farthest_vertices(net) #which two nodes are farthest
igraph::farthest_vertices(net, directed = F)

igraph::get_diameter(net) #which path is longest
igraph::get_diameter(net, directed = F)
```

```{r}
## distance####
distances(net)[1:10,1:10] #distances between dyads
mean_distance(net) #average distance for graph

```

```{r}
# information centrality####
# In general, actors with higher information centrality are predicted to
     # have greater control over the flow of information within a network.
# Highly information-central individuals tend to have a large number of 
     # short paths to many others within the social structure.
# In other words, the node is more likely to be hit 
     # when taking a random walk through the network
summary(infocent(net_sna))
summary(infocent(net_sna, rescale = T)) #rescale makes the centralities sum to 1
```




```{r}
#### CUG (Conditional Uniform Graph) Tests####
# CUG tests if graph is more clustered than we expect by chance (w&f, p 543-545)
  # Note: They can take a while to run.

# We simulate networks of the same size as our network (or density, or dyad census)
# Compare our network to the simulations
```

```{r}
# Test transitivity against density####
Cug_Edges <- sna::cug.test(net_sna, gtrans, cmode="edges")
plot(Cug_Edges)
Cug_Edges$obs.stat #our network
summary(Cug_Edges$rep.stat) # simulated networks
# ours is higher than simulations
```

```{r}
# Test Transitivity against the Dyad Census####
Cug_Dyad <- cug.test(net_sna, gtrans, cmode="dyad.census")
plot(Cug_Dyad)
Cug_Dyad$obs.stat #our network
summary(Cug_Dyad$rep.stat) # simulated networks
# ours is higher than simulations
```

```{r}
# Test Transitivity against the size####
Cug_size <- cug.test(net_sna, gtrans, cmode="size")
plot(Cug_size)
Cug_size$obs.stat #our network
summary(Cug_size$rep.stat) # simulated networks
# ours is lower than simulations
```

```{r}
# conclusion####
# Conclusion: transitivity is higher than expected given density and dyad census, 
     # but lower than expected for size
```

```{r}
### other functions####
# function must return a single value for the whole graph
# functions from sna package, not igraph, to work properly

centralization(net_sna, degree)
Cug_degcent <- cug.test(net_sna, FUN = function(net_sna) centralization(net_sna, degree), cmode = "edges")
plot(Cug_degcent)
Cug_degcent$obs.stat #our network
summary(Cug_degcent$rep.stat) # simulated networks
# ours is equivalent to the simulations
```

```{r}
centralization(net_sna, betweenness)
Cug_betcent <- cug.test(net_sna, FUN = function(net_sna) centralization(net_sna, betweenness), cmode = "edges")
plot(Cug_betcent)
Cug_betcent$obs.stat #our network
summary(Cug_betcent$rep.stat) # simulated networks
# ours is equivalent to the simulations
```

```{r}
centralization(net_sna, closeness)
Cug_clocent <- cug.test(net_sna, FUN = function(net_sna) centralization(net_sna, closeness), cmode = "edges")
plot(Cug_clocent)
Cug_clocent$obs.stat #our network
summary(Cug_clocent$rep.stat) # simulated networks
# ours is equivalent to the simulations
```



```{r}
gden(net_sna)
Cug_gden <- cug.test(net_sna, FUN = gden, cmode = "size")
plot(Cug_gden)
Cug_gden$obs.stat #our network
summary(Cug_gden$rep.stat) # simulated networks
# ours is lower than simulations
```

```{r}
components(net_sna)
Cug_comp <- cug.test(net_sna, FUN = components, cmode = "edges")
plot(Cug_comp)
Cug_comp$obs.stat #our network
summary(Cug_comp$rep.stat) # simulated networks
# ours is higher than simulations
```

```{r}
mean(degree(net_sna))
Cug_meandeg <- cug.test(net_sna, FUN = function(net_sna) mean(degree(net_sna)), cmode = "size")
plot(Cug_meandeg)
Cug_meandeg$obs.stat #our network
summary(Cug_meandeg$rep.stat) # simulated networks
# ours is lower than simulations
```

```{r}
grecip(net_sna)
Cug_recip <- cug.test(net_sna, FUN = grecip, cmode = "edges")
plot(Cug_recip)
Cug_recip$obs.stat #our network
summary(Cug_recip$rep.stat) # simulated networks
# ours is higher than simulations
```

```{r}
max(kcores(net_sna))
Cug_kcore <- cug.test(net_sna, FUN = function(net_sna) max(kcores(net_sna)), cmode = "size")
plot(Cug_kcore)
Cug_kcore$obs.stat #our network
summary(Cug_kcore$rep.stat) # simulated networks
# ours is lower than simulations
```

```{r}
#### components####
# igraph####
?igraph::components #look at details
comp <- igraph::components(net) #default is weak
comp
# membership - which component node is part of
# csize = size of components
# number of components
comp_w <- igraph::components(net, mode = "weak")
comp_w
comp_s <- igraph::components(net, mode = "strong")
comp_s

is_connected(net) #weakly connected
is_connected(net, mode = "strong") # strongly connected

count_components(net) #how many weak clusters
count_components(net, mode = "strong") #how many strong clusters

max_comp <- which.max(comp_s$csize)
max_comp #which component is largest

big_comp <- induced_subgraph(net, which(comp_s$membership == max_comp))
big_comp #keep only the largest connected component of the graph

```

```{r}
# sna####
?component.dist
sna_comp <- sna::component.dist(net_sna) #default is strong
sna_comp 
# membership - which component node is part of
# csize = size of components
# cdist = distribution of sizes
sna_comp_s <- sna::component.dist(net_sna, connected = "strong")
sna_comp_s
sna_comp_w <- sna::component.dist(net_sna, connected = "weak")
sna_comp_w

sna::components(net_sna) #how many strong components
sna::components(net_sna, connected = "strong") #30
sna::components(net_sna, connected = "weak") #1

```

```{r}
#### cliques####
?cliques
cliques(net) #cliques in the directed graph
cliques(un_net) #cliques in the undirected graph
cliques(net, min = 2) #cliques in the directed graph of at least size 3
cliques(un_net, min = 2) #cliques in the undirected graph of at least size 3

max_cliques(net, min = 2) # max cliques (can't be absorbed into larger clique) of at least size 3

igraph::clique_num(net) # size of largest clique
igraph::clique_num(un_net)
```

```{r}
#### k-core####
?coreness
kcore <- igraph::coreness(net)
kcore #core of each node (at least k degree)
table(kcore) # cores of network and how many nodes are involved (ex: 6 nodes have core of 5)
kcore_in <- igraph::coreness(net, mode = "in")
kcore_in #core of each node (at least k degree)
table(kcore_in) # cores of network and how many nodes are involved (ex: 6 nodes have core of 5)
kcore_out <- igraph::coreness(net, mode = "out")
kcore_out #core of each node (at least k degree)
table(kcore_out) # cores of network and how many nodes are involved (ex: 6 nodes have core of 5)

?kcores
kc <- sna::kcores(net_sna)
kc
table(kc)
kc_in <- kcores(net_sna, cmode="indegree") #degree of core calcuated on in ties
kc_in
table(kc_in)
kc_out <- kcores(net_sna, cmode="outdegree") #degree of core calcuated on out ties
kc_out
table(kc_out)
```

```{r}
#### cutpoints####
cp <- cutpoints(net_sna, mode = "digraph") #strong cut points in directed graph
cp

cp_weak <- cutpoints(net_sna, mode = "digraph", connected = "weak")
cp_weak
```

```{r}

```


```{r}
#### communities####
## Fluid clusters####
?cluster_fluid_communities 
set.seed(1)
cfc <- cluster_fluid_communities(un_net, no.of.communities = 4) #need simple, undirected networks
# specific the number of communities we want to find
# modularity(cfc) #modularity/partition
membership(cfc) #which community a node belongs to
length(cfc) #how many communities
sizes(cfc) #how many nodes in each community
```


```{r}
# data manipulation####
members <- membership(cfc) #pull membership
cfc_id <- data.frame(cfc_id = as.numeric(members), ego_id = as.numeric(names(members))) #create small dataset
nodes <- merge(nodes, cfc_id, by = 'ego_id', all = TRUE) #add to nodelist
```

```{r}
## Leading Eigenvector####
?cluster_leading_eigen
set.seed(1)
cle <- cluster_leading_eigen(un_net) #for undirected graphs
modularity(cle) 
membership(cle) 
length(cle)
sizes(cle)
```

```{r}
# plot####
colors <- colorpanel(length(cle), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cle))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(cle)
cle_id <- data.frame(cle_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, cle_id, by = 'ego_id', all = TRUE)
```

```{r}
## Walktrap####
?cluster_walktrap 
set.seed(1)
cwt <- cluster_walktrap(un_net)
modularity(cwt) 
membership(cwt) 
length(cwt)
sizes(cwt)
```

```{r}
# plot####
colors <- colorpanel(length(cwt), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cwt))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(cwt)
cwt_id <- data.frame(cwt_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, cwt_id, by = 'ego_id', all = TRUE)
```

```{r}
## Spinglass####
?cluster_spinglass
#^This function has a gamma parameter that we can tweak!!
set.seed(1)
csg <- cluster_spinglass(net)
modularity(csg) 
membership(csg) 
length(csg)
sizes(csg)
```

```{r}
# plot####
colors <- colorpanel(length(csg), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# tuning parameters####
set.seed(1)
csg_1 <- cluster_spinglass(net, gamma = 1.25)
length(csg_1)
csg_2 <- cluster_spinglass(net, gamma = 1.27)
length(csg_2)
csg_3 <- cluster_spinglass(net, gamma = 1.3)
length(csg_3)
csg_4 <- cluster_spinglass(net, gamma = 1.32)
length(csg_4)
csg_5 <- cluster_spinglass(net, gamma = 1.35)
length(csg_5)
csg_6 <- cluster_spinglass(net, gamma = 1.37)
length(csg_6)

colors <- colorpanel(length(csg_1), low = "#efd9d3", high = "#57424a")
csg_1_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_1))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_1))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(csg_2), low = "#efd9d3", high = "#57424a")
csg_2_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_2))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_2))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(csg_3), low = "#efd9d3", high = "#57424a")
csg_3_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_3))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_3))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(csg_4), low = "#efd9d3", high = "#57424a")
csg_4_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_4))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_4))), repel = T) +
  expand_limits(y = c(NA, 5.)) +  # Expands only the top (max y) to 2
  theme(legend.position = "none")

colors <- colorpanel(length(csg_5), low = "#efd9d3", high = "#57424a")
csg_5_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_5))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_5))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(csg_6), low = "#efd9d3", high = "#57424a")
csg_6_plot <- ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_6))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_6))), repel = T) +
  theme(legend.position = "none")

library(ggpubr)
ggarrange(csg_1_plot, csg_2_plot, csg_3_plot, csg_4_plot, csg_5_plot, csg_6_plot,
          nrow = 2, ncol = 3)
```
```{r}
csg_4_plot <- ggraph(net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_4))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_4))), repel = T) +
  expand_limits(y = c(NA, 5.5)) +  # Expands only the top (max y) to 2
  theme(legend.position = "none")
show(csg_4_plot)
```


```{r}
colors <- colorpanel(length(csg_6), low = "#efd9d3", high = "#57424a")
csg_6_plot <- ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg_5))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(csg_5))), repel = T) +
  theme(legend.position = "none")

library(ggpubr)
ggarrange(csg_6_plot)
```

```{r}
## Label Propagation Techniques####
?cluster_label_prop 
set.seed(1)
clp <- cluster_label_prop(net)
modularity(clp) 
membership(clp) 
length(clp)
sizes(clp)
```

```{r}
# plot####
colors <- colorpanel(length(clp), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clp))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(clp)
clp_id <- data.frame(clp_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, clp_id, by = 'ego_id', all = TRUE)
```

```{r}
## Optimal community structure####
?cluster_optimal
set.seed(1)
clo <- cluster_optimal(net)
modularity(clo) 
membership(clo) 
length(clo)
sizes(clo)
```

```{r}
# plot####
colors <- colorpanel(length(clo), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clo))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(clo)
clo_id <- data.frame(clo_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, clo_id, by = 'ego_id', all = TRUE)
```

```{r}
## Fast-Greedy Techniques####
?cluster_fast_greedy 
set.seed(1)
cfg <- cluster_fast_greedy(s_un_net) # error! We need to remove duplicated edges from our graph object
modularity(cfg) 
membership(cfg) 
length(cfg)
sizes(cfg)
```

```{r}
# plot####
colors <- colorpanel(length(cfg), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cfg))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(cfg)
cfg_id <- data.frame(cfg_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, cfg_id, by = 'ego_id', all = TRUE)
```

```{r}
## InfoMAP####
?cluster_infomap
set.seed(1)
cim <- cluster_infomap(net)
modularity(cim) 
membership(cim) 
length(cim)
sizes(cim)
```

```{r}
# plot####
colors <- colorpanel(length(cim), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cim))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# data manipulation####
members <- membership(cim)
cim_id <- data.frame(cim_id = as.numeric(members), ego_id = as.numeric(names(members)))
nodes <- merge(nodes, cim_id, by = 'ego_id', all = TRUE)
```

```{r}
## Louvain method####
?cluster_louvain 
# has resolution parameter we can tweak!
set.seed(1)
clv <- cluster_louvain(un_net)
modularity(clv) 
membership(clv) 
communities(clv)
length(clv)
sizes(clv)
```

```{r}
# plot####
colors <- colorpanel(length(clv), low = "#efd9d3", high = "#57424a")
ggraph(net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv))),
                  size = igraph::degree(net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")
```

```{r}
# tuning parameters####
set.seed(1)
clv_1 <- cluster_louvain(un_net, resolution = 0.7)
length(clv_1)
clv_2 <- cluster_louvain(un_net, resolution = 0.8)
length(clv_2)
clv_3 <- cluster_louvain(un_net, resolution = 0.9)
length(clv_3)
clv_4 <- cluster_louvain(un_net, resolution = 1)
length(clv_4)
clv_5 <- cluster_louvain(un_net, resolution = 1.25)
length(clv_5)
clv_6 <- cluster_louvain(un_net, resolution = 1.5)
length(clv_6)

colors <- colorpanel(length(csg_1), low = "#efd9d3", high = "#57424a")
clv_1_plot <- ggraph(un_net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_1))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_1))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(clv_2), low = "#efd9d3", high = "#57424a")
clv_2_plot <- ggraph(un_net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_2))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_2))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(clv_3), low = "#efd9d3", high = "#57424a")
clv_3_plot <- ggraph(un_net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_3))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_3))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(clv_4), low = "#efd9d3", high = "#57424a")
clv_4_plot <- ggraph(un_net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_4))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_4))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(clv_5), low = "#efd9d3", high = "#57424a")
clv_5_plot <- ggraph(un_net) +
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_5))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_5))), repel = T) +
  theme(legend.position = "none")

colors <- colorpanel(length(clv_6), low = "#efd9d3", high = "#57424a")
clv_6_plot <- ggraph(un_net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_6))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_6))), repel = T) +
  theme(legend.position = "none")

library(ggpubr)
ggarrange(clv_1_plot, clv_2_plot, clv_3_plot, clv_4_plot, clv_5_plot, clv_6_plot,
          nrow = 2, ncol = 3)
```

```{r}
colors <- colorpanel(length(clv_6), low = "#efd9d3", high = "#57424a")
clv_6_plot <- ggraph(un_net) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(clv_6))),
                  size = igraph::degree(un_net, mode = "all"), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  geom_node_text(aes(label = as.factor(membership(clv_6))), repel = T) +
  theme(legend.position = "none")
ggarrange(clv_6_plot)
```


```{r}
# Load libraries
library(igraph)
library(ggraph)
library(ggpubr)
library(grDevices)

# Create the network from your data
raw_data <- read.csv("COCAINE_DEALING.csv", check.names = FALSE)
row_names <- raw_data[, 1]
adj_matrix <- as.matrix(raw_data[, -1])
rownames(adj_matrix) <- row_names

# Create undirected network
un_net <- graph_from_adjacency_matrix(
  adj_matrix,
  mode = "undirected",
  weighted = TRUE,
  diag = FALSE
)

# Check components
comp <- components(un_net)
cat("=== Network Components ===\n")
cat("Number of components:", comp$no, "\n")
cat("Component sizes:", comp$csize, "\n")
cat("Nodes in main component:", sum(comp$membership == which.max(comp$csize)), "\n\n")

# METHOD: Use largest component without Kay
cat("=== Spinglass Clustering with Kay Isolated ===\n\n")

# Get adjacency matrix
adj_mat <- as.matrix(get.adjacency(un_net, attr = "weight", sparse = FALSE))

# Remove Kay
nodes_without_kay <- rownames(adj_mat)[rownames(adj_mat) != "Kay"]
adj_mat_no_kay <- adj_mat[nodes_without_kay, nodes_without_kay]

# Create network without Kay
net_no_kay <- graph_from_adjacency_matrix(
  adj_mat_no_kay,
  mode = "undirected",
  weighted = TRUE,
  diag = FALSE
)

# Check components of network without Kay
comp_no_kay <- components(net_no_kay)
cat("Network without Kay:\n")
cat("  Number of components:", comp_no_kay$no, "\n")
cat("  Component sizes:", comp_no_kay$csize, "\n")

# Get the largest component
largest_component <- which.max(comp_no_kay$csize)
nodes_in_largest <- V(net_no_kay)[comp_no_kay$membership == largest_component]
net_main <- induced_subgraph(net_no_kay, nodes_in_largest)

cat("  Using largest component with", vcount(net_main), "nodes\n\n")

# Try different gamma values on the MAIN COMPONENT
gamma_values <- c(0.5, 0.7, 0.9, 1.0, 1.2, 1.5)
results <- list()

for(i in seq_along(gamma_values)) {
  gamma <- gamma_values[i]
  set.seed(42)
  
  # Run spinglass on main component
  csg <- cluster_spinglass(net_main, gamma = gamma, weights = E(net_main)$weight)
  
  # Create membership vector for ALL original nodes
  full_membership <- setNames(rep(NA, vcount(un_net)), V(un_net)$name)
  
  # Assign cluster numbers to nodes in main component
  main_nodes <- V(net_main)$name
  full_membership[main_nodes] <- membership(csg)
  
  # Assign nodes in other components to their own clusters
  other_components <- setdiff(1:comp_no_kay$no, largest_component)
  next_cluster <- max(full_membership, na.rm = TRUE) + 1
  
  for(comp_id in other_components) {
    comp_nodes <- V(net_no_kay)[comp_no_kay$membership == comp_id]$name
    full_membership[comp_nodes] <- next_cluster
    next_cluster <- next_cluster + 1
  }
  
  # Assign Kay to her own cluster
  full_membership["Kay"] <- next_cluster
  
  # Create custom community object
  final_clusters <- make_clusters(un_net, membership = full_membership)
  
  # Store results
  results[[i]] <- list(
    gamma = gamma,
    clusters = final_clusters,
    n_communities = length(unique(na.omit(full_membership))),
    modularity = modularity(final_clusters),
    kay_cluster = full_membership["Kay"]
  )
  
  cat(sprintf("Gamma = %.1f: %d communities, Modularity = %.3f, Kay in cluster %d\n", 
              gamma, results[[i]]$n_communities, results[[i]]$modularity, 
              results[[i]]$kay_cluster))
}

# Find best gamma
best_idx <- which.max(sapply(results, function(x) x$modularity))
best_result <- results[[best_idx]]
cat(sprintf("\nBest gamma: %.1f (modularity = %.3f)\n", 
            best_result$gamma, best_result$modularity))

# Show cluster composition
best_clusters <- best_result$clusters
membership_vec <- membership(best_clusters)

cat("\nCluster composition:\n")
for(clust in sort(unique(membership_vec))) {
  nodes_in_clust <- names(membership_vec[membership_vec == clust])
  if("Kay" %in% nodes_in_clust) {
    cat(sprintf("  Cluster %d (Kay's cluster): %s\n", clust, paste(nodes_in_clust, collapse=", ")))
  } else {
    cat(sprintf("  Cluster %d (%d nodes): %s\n", 
                clust, 
                length(nodes_in_clust),
                paste(nodes_in_clust[1:min(5, length(nodes_in_clust))], collapse=", ")))
  }
}

# Visualize
n_comm <- length(unique(membership_vec))

# Create color palette - make Kay's cluster skyblue
if(n_comm > 1) {
  colors <- colorpanel(n_comm - 1, low = "#efd9d3", high = "#57424a")
  all_colors <- c(colors, "skyblue")
} else {
  all_colors <- c("skyblue")
}
names(all_colors) <- sort(unique(membership_vec))

# Plot
ggraph(un_net, layout = "stress") +
  geom_edge_link0(color = "gray70", alpha = 0.2) +
  geom_node_point(
    aes(fill = as.factor(membership(best_clusters)),
        size = igraph::degree(un_net)),
    color = "black", 
    shape = 21
  ) +
  scale_fill_manual(values = all_colors) +
  geom_node_text(
    aes(label = ifelse(name == "Kay", "KAY", 
                       ifelse(igraph::degree(un_net) > 3 & 
                                !is.na(membership(best_clusters)) & 
                                membership(best_clusters) != best_result$kay_cluster, 
                              name, ""))),
    repel = TRUE,
    size = ifelse(V(un_net)$name == "Kay", 5, 3),
    fontface = ifelse(V(un_net)$name == "Kay", "bold", "plain"),
    color = "black"
  ) +
  scale_size_continuous(range = c(2, 10)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none") +
  labs(title = paste("Drug Dealer Network - Kay Isolated (γ =", best_result$gamma, ")"),
       subtitle = paste("Kay (skyblue) alone |", n_comm, "total communities | Modularity =", 
                        round(best_result$modularity, 3)))
```

```{r}
# Assuming you already have:
# - un_net (your network)
# - best_clusters (the community object with Kay isolated)

# Create color palette
n_comm <- length(unique(membership(best_clusters)))
colors <- colorpanel(n_comm, low = "#efd9d3", high = "#57424a")

# Make Kay's cluster skyblue
kay_cluster <- membership(best_clusters)["Kay"]
colors[kay_cluster] <- "skyblue"

# Create hierarchical layout plot
csg_kay_hierarchical <- ggraph(un_net, layout = "dendrogram", circular = FALSE) +
  geom_edge_diagonal(color = "black", alpha = 0.3) +
  geom_node_point(aes(fill = as.factor(membership(best_clusters))),
                  size = 4, 
                  color = "black", 
                  shape = 21) +
  scale_fill_manual(values = colors) +
  geom_node_text(aes(label = as.factor(membership(best_clusters))),
                 repel = FALSE,
                 size = 3,
                 nudge_y = 0.1) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none",
        plot.margin = margin(1, 1, 1, 1, "cm"))

# Display
csg_kay_hierarchical
```


```{r}
#### Compare Partitions####
modularities <- c(
            eigen = modularity(cle),
            walk = modularity(cwt),
            spinglass = modularity(csg_1),
            label = modularity(clp),
            optimal = modularity(clo),
            fastgreed = modularity(cfg),
            infomap = modularity(cim),
            louvain = modularity(clv))
modularities # optimal has highest modularity
which.max(modularities) # optimal has highest modularity

# Other measures
vi <- compare(cle, cwt, method = "vi") 
vi
# "variation of information" tells you about the theoretical distance between communities. Basically, what it would take (a lot, nothing) to turn one community assignment into another. 
# Range of values: 0-ln(n) (0 is identical, higher is more different)
nmi <- compare(cle, cwt, method = "nmi") 
nmi
# "normalized mutual information" (older measure) is a test similarity between partitions based on shared info. 
# Range of values: 0-1 (0 is independent, 1 is identical). It does not correct for chance agreement.
# It can be artificially high if you have a lot of tiny communities.
sj <- compare(cle, cwt, method = "split.join") 
sj
# "split join" is a measure of how much tweaking of the network (splitting/merging communities) it would take to chance one partition into another. 
# Range of values: 0-inf (0 is identical, higher values mean more changes are needed). 
ar <- compare(cle, cwt, method = "adjusted.rand") 
ar
# "adjusted rand" is a pairwise comparison of whether 2 nodes should be in the same community. 
# Range of values: -1 to 1 (0 is chance, 1 is identical, -1 is worse than random). It does correct for chance agreement.

library(aricode)
m_cle <- igraph::membership(cle)
m_cwt <- igraph::membership(cwt)
m_cle <- as.integer(unlist(m_cle, use.names = FALSE))
m_cwt <- as.integer(unlist(m_cwt, use.names = FALSE))
ami <- AMI(m_cle, m_cwt) 
ami
# "adjusted mutual information" tests how much two partitions share. It is robust to different numbers of communities.  
# Range of values: 0-1. (0 is chance overlap, 1 is identical). It does correct for chance agreement. 
```

```{r}
#### Add self-loops####
# make sure you have a weight column (might not work properly if you don't), 
# and you may want to reduce your data to just ego, alter, and weight (in that order)
# may need to rename third column to "weight" depending on which version of R/packages you're using
modularity(cluster_fast_greedy(s_un_net)) # mod = 0.68
igraph::any_loop(s_un_net) #no loops
which_loop(s_un_net) # there are none
v1 <- get.data.frame(s_un_net, what = "vertices") #extract the node data from the object
summary(v1)
e1 <- get.data.frame(s_un_net, what = "edges")  #extract the edge data from the object
summary(e1) #we have a weight column. Good. 
length(cluster_fast_greedy(s_un_net)) # 8 clusters at baseline

s_un_net[from=V(s_un_net), to=V(s_un_net)] <- 5 #add weights of 5 to self-loops
modularity(cluster_fast_greedy(s_un_net)) # mod = 0.75
igraph::any_loop(s_un_net) # now there are loops
which_loop(s_un_net) #these ones
v2 <- get.data.frame(s_un_net, what = "vertices")
summary(v2)
e2 <- get.data.frame(s_un_net, what = "edges")
summary(e2) #there are 63 more edges (as there should be, because there are 63 nodes in the data)
length(cluster_fast_greedy(s_un_net)) # now 9

s_un_net[from=V(s_un_net), to=V(s_un_net)] <- 10 #add heavier self-loops
modularity(cluster_fast_greedy(s_un_net)) # mod = 0.79; getting higher with heavier weights
igraph::any_loop(s_un_net)
which_loop(s_un_net)
v3 <- get.data.frame(s_un_net, what = "vertices")
summary(v3)
e3 <- get.data.frame(s_un_net, what = "edges")
summary(e3) #now the weights for the self-loops are 10
length(cluster_fast_greedy(s_un_net)) # now 11

```

```{r}
#### packages####
library(lme4)
library(lmerTest)
library(gplots)
library(dplyr)
library(igraph)
```

```{r}
## variables####
# contextual effect
edges3 <- edges3 %>%
  group_by(ego_id) %>%
  dplyr::mutate(net_age = mean(age_alter)) #calculate the contextual effect
summary(edges3)

# network descriptive
nodes$deg <- igraph::degree(net, mode = "all") #calculate network descriptive
nodes$deg

names(nodes)
names(edges3)
edges4 <- merge(nodes, edges3, by = "ego_id") #merge again to add degree
```

```{r}
#### Egocentric Analysis####
summary(edges4)
```

```{r}
### 1. Random intercept model with covariates####
#model1 <- lm(weight ~ age_ego + gender_ego + 
          #       age_alter + gender_alter, # + (1 | ego_id), # code between parentheses are the random effects
          #     data = edges4, #REML = T, 
          #     na.action = na.omit)
#summary(model1)

model1 <- lmer(weight ~ age_ego + gender_ego + 
                 age_alter + gender_alter + (1 | ego_id), # code between parentheses are the random effects
               data = edges4, REML = T, 
               na.action = na.omit)
summary(model1)
# Reduction in tie closeness for older alters and male alters (ignoring significance)
# Increase in tie closeness for older egos and male egos (ignoring significance)
```



```{r}
## Intraclass correlation####
# ICC is the level-2 variance divided by the total variance
# this variance comes from the random effects (at the top of the mlm output)

0.2417/(0.2417 + 1.1642) 
# it's fairly low (range is 0 to 1), which indicates that there is a lot of variation around the level-2 observation

library(performance)
performance::icc(model1) # you can also have it calculated automatically
# the conditional ICC also accounts for the fixed effects (adjusted is just random effects), 
# but you don't have to worry about that. Adjusted ICC is (usually) enough
```

```{r}
### 2. Random intercept model with contextual effect####
model2 <- lmer(weight ~ age_ego + gender_ego + 
                 age_alter + gender_alter + 
                 net_age + (1 | ego_id),
               data = edges4, REML = T, 
               na.action = na.omit)
summary(model2)
# as the ego's network gets older, their relationships get closer (ignoring significance)
```

```{r}
## Intraclass correlation####
performance::icc(model2) # still pretty small; lots of variation around ego
```

```{r}
### 3. Random coefficient model####
model3 <- lmer(weight ~ age_ego + gender_ego + 
                 age_alter + gender_alter + 
                 net_age + (age_alter | ego_id), # alter_age (level-1 variable) is random slope
               data = edges4, REML = T,
               na.action = na.omit) #this is hard to fit on data this small
summary(model3) 
# warning that there is a singular fit
# singular fits can be from over fitting / random effects being near zero or correlations being ~1
# this is probably due to this data being unable to support random effects that are this complex
```

```{r}
compare_optimizers <- allFit(model3) # it's possible that this it's a false positive, so you can check
# comparing different model optimizers can be informative
summary(compare_optimizers)$llik # these are all basically the same, which is a good sign
summary(compare_optimizers)$fixef # optimx.L-BFGS-B (and a little bit nloptwrap.NLOPT_LN_BOBYQA) are different

# # https://joshua-nugent.github.io/allFit/
# optimx_options <- c("L-BFGS-B", "nlminb", "nlm", "bobyqa", "nmkb", "hjkb")
# for(i in 1:length(optimx_options)){
#   print(paste0("Testing optimx: ", optimx_options[i]))
#   tryCatch({
#     model_flex <- lmer(weight ~ age_ego + gender_ego + age_alter + gender_alter +
#                          net_age + (age_alter | ego_id),
#                        data = edges4, REML = T,
#                        na.action=na.omit,
#                        control = lmerControl(optimizer = "optimx",
#                                              optCtrl = list(method = optimx_options[i],
#                                                             maxit = 1e9)))
#     if(is.null(model_flex@optinfo$conv$lme4$messages)){
#       print(paste0("One of the optimx options, ", optimx_options[i], ", worked!"))
#       print(model_flex)
#       break
#       } else {
#         print(paste0("Convergence issue with optimx option: ", optimx_options[i]))
#         }
#     }, error = function(e) {
#       print(paste0("Error occurred with optimx option: ", optimx_options[i], ": ", e$message))
#       })
#   } # another option

# scaling and centering can also help with some kinds of model fit issues
table(edges4$age_ego)
table(edges4$age_alter)
table(edges4$net_age)

edges4$age_ego_scale <- scale(edges4$age_ego, center = T, scale = T) #center subtracts the mean, scale divides by the standard deviation
edges4$age_alter_scale <- scale(edges4$age_alter, center = T, scale = T) #center subtracts the mean, scale divides by the standard deviation
edges4$net_age_scale <- scale(edges4$net_age, center = T, scale = T) #center subtracts the mean, scale divides by the standard deviation
```

```{r}
# Choose one of the good optimizers and run again
model3b <- lmer(weight ~ age_ego + gender_ego + 
                 age_alter + gender_alter + 
                 net_age + (age_alter | ego_id), 
               data = edges4, REML = T,
               control = lmerControl(optimizer = "bobyqa"),
               na.action = na.omit)
summary(model3b) # similar to model 3 and has a warning
mods <- list(model3, model3b)
sjPlot::tab_model(mods) #to make a pretty table; can further adjust this to make it look better
```

```{r}
## Intraclass correlation####
performance::icc(model3b) # because of the singularity warning, default doesn't work
performance::icc(model3b, tolerance = 0) #setting the tolerance to 0 makes the test less strict, which allows it to run
# ^ pretty small; lots of variation
```

```{r}
### 4. cross-level interaction####
model4 <- lmer(weight ~ age_ego*net_age + gender_ego + # multiply variables to interact
                 age_alter*net_age + gender_alter + 
                 net_age + (age_alter | ego_id),
               data = edges4, REML = T,
               control = lmerControl(optimizer = "bobyqa"),
na.action = na.omit) #this is hard to fit on this data
summary(model4) 
# convergence warning
# no significant interactions
m4Fit <- allFit(model4)
m4Fit
summary(m4Fit)$llik #pretty close to the same
summary(m4Fit)$fixef #nmkbw, optimx.L-BFGS-B, and nloptwrap.NLOPT_LN_BOBYQA are somewhat different

# model4b <- lmer(weight ~ age_ego*net_age + gender_ego + 
#                  age_alter*net_age + gender_alter + 
#                  net_age + (age_alter | ego_id),
#                data = edges4, REML = T,
#                control=lmerControl(optimizer = "bobyqa", 
#                                    check.conv.singular = .makeCC(action = "message",  
#                                                                  tol = 1e-4)),
#                na.action = na.omit)
# summary(model4b) # still have issues with convergence, but I'm ignoring them by hiding the message
# # no significant interactions
```

```{r}
library(sjPlot) # I prefer to visualize interactions, and this package helps
sjPlot::plot_model(model4, type = "pred", terms = c("net_age", "age_alter"))
sjPlot::plot_model(model4, type = "pred", terms = c("net_age", "age_ego"))
# ^ these visualizations show that the interactions aren't significant; lots of overlap
```

```{r}
## Intraclass correlation####
performance::icc(model4, tolerance = 0) #pretty small
```

```{r}
### 5. Add network descriptives####
model5 <- lmer(weight ~ age_ego*net_age + gender_ego + 
                  age_alter*net_age + gender_alter + 
                  net_age + deg +
                  (age_alter | ego_id),
                data = edges4, REML = T,
               control = lmerControl(optimizer = "bobyqa"),
                na.action = na.omit)
summary(model5) # still have issues with convergence
# As degree increases, relationship strength gets weaker

# model5 <- lmer(weight ~ age_ego*net_age + gender_ego + 
#                   age_alter*net_age + gender_alter + 
#                   net_age + deg +
#                   (age_alter | ego_id),
#                 data = edges4, REML = T,
#                 control=lmerControl(optimizer = "bobyqa", 
#                                     check.conv.singular = .makeCC(action = "ignore",  
#                                                                   tol = 1e-4)),
#                 na.action = na.omit)
# summary(model5) # still have issues with convergence, but I'm ignoring them
# As degree increases, relationship strength gets weaker

```

```{r}
## Intraclass correlation####
performance::icc(model5, tolerance = 0) # pretty small
```

```{r}
### anova####
# We can to compare our model fits
anova(model5, model4) # p-value < 0.05; a significant improvement in model fit in 5 vs 4!
anova(model5, model3b) # p-value > 0.05; not a significant improvement in model fit 5 vs 3
anova(model5, model2) # p-value > 0.05; not a significant improvement in model fit 5 vs 2
anova(model5, model1) # p-value > 0.05; not a significant improvement in model fit 5 vs 1
anova(model4, model3b) # p-value > 0.05; not a significant improvement in model fit 4 vs 3
anova(model4, model2) # p-value > 0.05; not a significant improvement in model fit 4 vs 2
anova(model4, model1) # p-value > 0.05; not a significant improvement in model fit 4 vs 1
anova(model3b, model2) # p-value > 0.05; not a significant improvement in model fit 3 vs 2
anova(model3b, model1) # p-value > 0.05; not a significant improvement in model fit 3 vs 1
anova(model2, model1) # p-value > 0.05; not a significant improvement in model fit 1 vs 2

# Based on these results, model 5 seems like the best fit
mods <- list(model5, model4, model3b, model2, model1)
sjPlot::tab_model(mods) #can further adjust this to make it look better
```

```{r}
model1 <- ergm(net_sna ~ edges)
summary(model1)
```

```{r}
mod_sum <- summary(model1) #save summary as an object
mod_sum
beta <- coef(mod_sum)[1] #extract the estimate
beta <- mod_sum$coefficients[1] #this also works
beta #this is the coefficient for the edges term

prob <- exp(beta)/(1+exp(beta)) #calculate the probability of forming a tie
prob # the probability of forming a tie with someone else at random is 4.5%

plogis(mod_sum$coefficients[1]) # if you don't want to calculate the probability manually, you can also use the plogis command
plogis(beta) #this also works, based on the object created above
plogis(coef(model1)[['edges']]) # alternatively, you can extra the coefficient from the model this way and get the probability

gden(net_sna)
```
```{r}
gof.model1_btergm <- btergm::gof(model1, nsim = 100, # checking goodness of fit of model estimates against 100 simulated networks
                                   statistics = c(esp, deg, odeg, ideg, geodesic, 
                                                  triad.directed, fastgreedy.modularity)) #picked these statistics
gof.model1_btergm # extract tables. For those with p-values, the closer to 1 the better the fit
# Edge-wise shared partners - how many alters do two tied nodes have in common
# Degree - number of ties
# Outdegree - number of outgoing ties *0 fits poorly
# Indegree - number of incoming ties
# Geodesic distances - shortest distance through graph *3, 4, inf fit poorly
# Triad Directed - triad census for directed graph
# Fast-Greedy Modularity - community detection modularity for Fast-Greedy

gof.model1_btergm$Degree$stats #can look at one measure alone

plot(gof.model1_btergm)
```
```{r}
net <- igraph::graph_from_data_frame(edges, directed = F, vertices = nodes)
net
```

```{r}
param <- param.dcm(inf.prob = 0.5, act.rate = 0.5) 
# inf.prob = prob of infection, act.rate = avg. num. transmissible acts per person per unit time
init <- init.dcm(s.num = 28, i.num = 1)
# s.num = num initally susceptible, i.num = num initial infection
control <- control.dcm(type = "SI", nsteps = 40)
```

```{r}
si_mod <- dcm(param, init, control)

# If we look at the model object we can see some of the basic details about our choices. 

si_mod
```
```{r}
plot(si_mod)
```

```{r}
si_mod_df <- as.data.frame(si_mod)
```

```{r}
plot(si_mod)
plot(si_mod, y = "s.num")
plot(si_mod, y = "i.num")
plot(si_mod, y = "si.flow")
```

```{r}
ggplot(si_mod_df) + 
  geom_line(aes(x = time, y = s.num), colour="#1A1A1A", size = 1, linetype = "solid") +
  geom_line(aes(x = time, y = i.num), colour="#4A4A4A", size = 1, linetype = "dashed") +
  geom_line(aes(x = time, y = si.flow), colour="#8A8A8A", size = 1, linetype = "dotted") +
  scale_x_continuous(limits = c(0,40), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,30), expand = c(0, 0)) +
  xlab("Time") + 
  ylab("Dynamics") +
  theme_classic(base_size = 12)
```

```{r}
param <- param.dcm(inf.prob = 0.2, act.rate = 0.25, rec.rate = 0.02)
init <- init.dcm(s.num = 63, i.num = 1)
control <- control.dcm(type = "SIS", nsteps = 50)
sis_mod <- dcm(param, init, control)

sis_mod

```
```{r}
param <- param.dcm(inf.prob = 0.2, act.rate = 0.25, rec.rate = 0.02)
init <- init.dcm(s.num = 28, i.num = 1)
control <- control.dcm(type = "SIS", nsteps = 40)
sis_mod <- dcm(param, init, control)

sis_mod
```

```{r}
# We can look at the model details by opening the details of the model into a dataframe. 
# With this, we can see each of the variables at each point in time. 
sis_mod_df <- as.data.frame(sis_mod)
# head(sis_mod_df) #this creates a VERY long list, so I'm not printing it
```

```{r}
# We can also plot each of these variables (which I prefer)
plot(sis_mod)
plot(sis_mod, y = "si.flow")
plot(sis_mod, y = "is.flow")
plot(sis_mod, y = "s.num")
plot(sis_mod, y = "i.num")
```

```{r}
# As I prefer ggplot aesthetics, I used the dataframe I made above for plotting. 
# And this way I can easily see each of the variables on the same plot.
# sis_mod_df #this creates a VERY long list, so I'm not printing it
colorpanel(4, low = "#EFD9D3", high = "#57424A")
ggplot(sis_mod_df) + 
  geom_line(aes(x = time, y = s.num), colour="#EFD9D3") +
  geom_line(aes(x = time, y = i.num), colour="#BCA7A5") +
  geom_line(aes(x = time, y = si.flow), colour="#8A7478") + 
  geom_line(aes(x = time, y = is.flow), colour="#57424A") +
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,100), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
```

```{r}
# Though, because the transition states are on a much different scale, it might be 
# worthwhile to make two plots - one for SI compartments, and one for transitions.
sis_p2 <- ggplot(sis_mod_df) + 
  geom_line(aes(x = time, y = s.num), colour="#EFD9D3") +
  geom_line(aes(x = time, y = i.num), colour="#BCA7A5") +
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,50), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
sis_p3 <- ggplot(sis_mod_df) + 
  geom_line(aes(x = time, y = si.flow), colour="#8A7478") +
  geom_line(aes(x = time, y = is.flow), colour="#57424A") +
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,1), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
ggarrange(sis_p2, sis_p3 + rremove("y.title"), ncol = 2)
# because both plots have the same y axis title, we can remove it from the second plot
```

```{r}
# In addition, to find the details of the model specific to a moment in time by using the
# summary function, like this:
summary(sis_mod, at = 25)
```

## SIR Model####
The last model type we'll discuss is the SIR model. Differently from the SIS model, 
this model has a third compartment for those who have RECOVERED from the infection.

```{r}
# To build the SIR model, we need to change two pieces of information. 
# We need to set the type to SIR in the control.dcm function. 
# We also need the r.num argument in the init.dcm function to represent the number 
# of people who are initially recovered for the infection. (Ordinarily this is 0.)
# Last, we need to set the rec.rate in the param.dcm function. 
# rec.rate determines the mean recovery rate for the SIR model. 
param <- param.dcm(inf.prob = 1/5, act.rate = 1, rec.rate = 1/20)
init <- init.dcm(s.num = 28, i.num = 1, r.num = 0)
control <- control.dcm(type = "SIR", nsteps = 50)
sir_mod <- dcm(param, init, control)
```

```{r}
# Like the prior models, we can examine the object and then plot the results. 
sir_mod_df <- as.data.frame(sir_mod)
# head(sir_mod_df) #this creates a VERY long list, so I'm not printing it
```

```{r}
# The sir model object has new variables to account for: r.num and ir.flow
# r.num is the number of recovered individuals
# ir.flow is the number of individuals transitioning from infected to recovered

plot(sir_mod, y = c("s.num", "i.num", "r.num", "si.flow", "ir.flow"))
```

```{r}
# As I prefer ggplot aesthetics, I used the dataframe I made above for plotting. 
# And this way I can easily see each of the variables all on the same plot.
colorpanel(5, low = "#EFD9D3", high = "#57424A")
ggplot(sir_mod_df) + 
  geom_line(aes(x = time, y = s.num), colour="#EFD9D3") +
  geom_line(aes(x = time, y = i.num), colour="#C9B3B1") + 
  geom_line(aes(x = time, y = r.num), colour="#A38E8F") + 
  geom_line(aes(x = time, y = si.flow), colour="#7D686C") +
  geom_line(aes(x = time, y = ir.flow), colour="#57424A") +
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,100), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
```

```{r}
# Though, because the transition states are on a much different scale, it might be 
# worthwhile to make two plots - one for SI compartments, and one for transitions.
sir_p2 <- ggplot(sir_mod_df) + 
  geom_line(aes(x = time, y = s.num), colour="#EFD9D3") + #lightest
  geom_line(aes(x = time, y = i.num), colour="#C9B3B1") + #medium
  geom_line(aes(x = time, y = r.num), colour="#A38E8F") + #medium
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,100), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
sir_p3 <- ggplot(sir_mod_df) + 
  geom_line(aes(x = time, y = si.flow), colour="#7D686C") + #dark
  geom_line(aes(x = time, y = ir.flow), colour="#57424A") + #dark
  scale_x_continuous(limits = c(0,50), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,2.5), expand = c(0, 0)) +
  xlab("Time") + ylab("Dynamics") +
  theme_classic()
ggarrange(sir_p2, sir_p3 + rremove("y.title"), ncol = 2)
# because both plots have the same y axis title, we can remove it from the second plot
```

```{r}
# In addition to find the details of the model specific to a moment in time by using the
# summary function, like this:
summary(sir_mod, at = 10)
```

```{r}
# We can plot that information using the comp_plot function. 
# This function allows us to see a flow chart of what our model is doing. 
comp_plot(sir_mod, at = 10)
# To make the plot cleaner, we can set the number of digits for the plot like this:
comp_plot(sir_mod, at = 10, digits = 0)
```

# igraph SIR Model####
If you want to plot the SIR model over an observed graph, 
I think the most straightforward way to do that is the use the SIR function in igraph. 

```{r}
# I'm using the illustrative network I've been using throughout the term. 

# One snafu with the igraph function is that it requires the graph to be "simple". 
# Simplified graphs do not have any loops or multiplex ties. 
is_simple(net) 
# Our graph is NOT simple, so we need to make it so. 
net <- igraph::simplify(net)
is_simple(net) 

# The arguments in the igraph sir function are different than those in the EpiModel package.
# Here, we set the rate of infection with the beta argument, and the rate of recovery is set by gamma.
```

```{r}
# (More specifically, per the igraph documentation, beta is:
# "The rate of infection of an individual 
# that is susceptible and has a single infected neighbor. 
# The infection rate of a susceptible individual with n infected neighbors is n times beta. 
# Formally this is the rate parameter of an exponential distribution."

# And gamma is: "The rate of recovery of an infected individual. 
# Formally, this is the rate parameter of an exponential distribution.")

set.seed(2)
sm50 <- sir(graph = net, beta = 5, gamma = 2) 
class(sm50)
# The object you get is not a dataframe, but an sir object. 
# So we need to use some tricks to take a look at it.
# The simplest approach is to use indexing. 
# head(sm50) #whole object,  #this creates a VERY long list, so I'm not printing it
sm50[[1]] #the first simulation
sm50[[1]]$times #times of events
sm50[[1]]$NS #number susceptible
sm50[[1]]$NI #number infected
sm50[[1]]$NR #number recovered
# plot(sm50) #plotting all simulations at once, default measure (NI)
par(mfrow = c(1, 3))
plot(sm50, comp = "NS") #plotting all simulations at once, for susceptible
plot(sm50, comp = "NI") #plotting all simulations at once, for infected (default)
plot(sm50, comp = "NR") #plotting all simulations at once, for recovered

plot(sm50, comp = "NS", xlim = c(0, 5), ylim = c(0, 75)) #set axes to better compare plots
plot(sm50, comp = "NI", xlim = c(0, 5), ylim = c(0, 75)) #set axes to better compare plots
plot(sm50, comp = "NR", xlim = c(0, 5), ylim = c(0, 75)) #set axes to better compare plots
```

```{r}
# (There may be a better way to do this, but this is what I came up with.) 
# Because I like to plot in ggplot, I needed to manipulate the list into a dataframe. 
# I only wanted to look at the first simulation, so first I created an object of just sim1. 
sm50_sim1 <- sm50[[1]]
names(sm50_sim1)
class(sm50_sim1)
# Then I unlisted that object into separate dataframes for each variable...
# list2env(setNames(sm50_sim1, paste0("df", seq_along(sm50_sim1))), envir = parent.frame()) #use this if not in markdown file
list2env(setNames(sm50_sim1, paste0("df", seq_along(sm50_sim1))), envir = environment()) 
# ...and recombined them into a new dataframe.
df50 <- data.frame(df1, df2, df3, df4)
# Unfortunately, in that process I lost the names of the variables, so I added them back.
df50b <- df50 %>% 
  dplyr::rename(times = df1,
                NS = df2, 
                NI = df3, 
                NR = df4)
```

```{r}
# Now I can plot like I prefer to.
colorpanel(3, low = "#EFD9D3", high = "#57424A")
b50_plot <- ggplot(df50b) +                    # basic graphical object
  geom_line(aes(x = times, y = NS), colour="#EFD9D3") + #lightest
  geom_line(aes(x = times, y = NI), colour="#A38E8F") + #medium
  geom_line(aes(x = times, y = NR), colour="#57424A") + #dark
  scale_x_continuous(limits = c(0, 4), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 35), expand = c(0, 0)) +
  xlab("time") + ylab("population") +
  theme_classic()
b50_plot
```

# Threshold models####
Threshold models are better for things that spread with complex contagion (ideas, behaviors, innovations). 

netdiffuseR is the best package I've seen for this, but updates have been sporatic in recent years.
More info can be found about it here: https://github.com/USCCANA/netdiffuseR

```{r}
net
net_sna_adj <- as_adjacency_matrix(net) # the function needs a matrix, not an igraph or sna object
n_nodes <- nrow(net_sna_adj)  # Should be 63
n_nodes
```

```{r}
# Get your network as an adjacency matrix
adj_mat <- as.matrix(get.adjacency(un_net, sparse = FALSE))

# Basic model with minimal parameters

diffnet_simple <- rdiffnet(
  n = nrow(adj_mat),
  t = 20,
  seed.nodes = which(V(un_net)$name == "Kay"),
  seed.p.adopt = 0.20,
  exposure.args = list(normalized = TRUE)
)



summary(diffnet_simple)
```
```{r}
plot_adopters(diffnet_simple, what = "cumadopt", include.legend = FALSE)
```


There is a single function that allows for a wide range of tweaks to the diffusion process. 
```{r}
# n = num. nodes
# t = num. time points
# seed.graph = starting graph for simulation (small-world, scale-free, bernoulli/er)
# rgraph.args = args for rgraph (ex: probability of tie formation)
# seed.nodes = character or vector (specific nodes, or location in network [random, central, marginal])
# seed.p.adopt = % early adopters
# rewire = T/F network rewired
# threshold.dist = adoption threshold for nodes
# exposure.args = args for exposure (ex: count or proportion)

diffnet_sw <- rdiffnet(
  n = 28, #63 nodes
  t = 10, # 10 time points
  seed.graph = "small-world", #small-world graph
  rgraph.args = list(p = 0.3), #30% tie probability
  seed.nodes = c(1, 25, 50), # chosen nodes
  seed.p.adopt = 0.1, #10% early adopters
  rewire = F, #rewire the network
  threshold.dist = function(i) 0.25, # % alters that need to adopt before ego will
  exposure.args = list(normalized = T) #rather than having exposure be a count, it's a proportion
)
diffnet_sw
# a few details - 100% adopted by the end of the time
summary(diffnet_sw) 
# period = point in time
# adopters = how many nodes adopted
# cum. adopt. % = proportion adopers
# hazard rate = prob. node adopts if it hasn't yet
# density = network density
# moran's I = spatial autocorrelation of adoption
  # pos = clusterd
  # neg = dispersed
  # sig = significant clustering or not?
# left censoring = at t1, how many adopters?
# right censoring = at end, how many non-adopters?
# num. nodes
table(diffnet_sw$toa) # time of adoption
plot_diffnet(diffnet_sw, slices = c(1, 5, 10))
plot_adopters(diffnet_sw, what = "adopt")
plot_adopters(diffnet_sw, what = "cumadopt", include.legend = FALSE)

set.seed(1)
diffnet_il <- rdiffnet(
  # n = 63, #don't need because we're using a real graph
  t = 10, 
  seed.graph = net_sna_adj,
  # rgraph.args = list(p = 0.3), #don't need because we're using a real graph
  seed.nodes = c(1, 25, 50), # chosen nodes
  seed.p.adopt = 0.1,
  rewire = F,
  threshold.dist = function(i) 0.25, 
  exposure.args = list(normalized = T)
  )
diffnet_il
summary(diffnet_il)
table(diffnet_il$toa) # time of adoption
plot_diffnet(diffnet_il, slices = c(1, 5, 10))
plot_adopters(diffnet_il, what = "adopt")
plot_adopters(diffnet_il, what = "cumadopt", include.legend = FALSE)
```

Plot the adoption curves
```{r}
cumadopt_sw <- cumulative_adopt_count(diffnet_sw)["prop", ]
cumadopt_il <- cumulative_adopt_count(diffnet_il)["prop", ]

adopt_data <- data.frame(
  time = rep(1:length(cumadopt_sw), 2),
  adopters = c(cumadopt_sw, cumadopt_il),
  diffusion = rep(c("Diffusion SW", "Diffusion Il"), each = length(cumadopt_sw))
)

ggplot(adopt_data, aes(x = time, y = adopters, color = diffusion)) +
  geom_line(size = 1.2, alpha = 0.5) +
  labs(x = "Time", y = "Proportion of Adopters", 
       title = "Comparison of Simulated vs Real Graph Diffusion") +
  theme_minimal()
```

Check network attributes
```{r}
## find path-length of the two graphs - SW should be lower, which enhances spread
sw_nets <- diffnet_to_igraph(diffnet_sw, slices=c(1:10))
sw_net_t1 <- sw_nets[[1]]  # Network at time 1

il_nets <- diffnet_to_igraph(diffnet_il, slices=c(1:10))
il_net_t1 <- il_nets[[1]]  # Network at time 1

mean_distance(sw_net_t1, directed = T)
is_directed(sw_net_t1)
mean_distance(il_net_t1, directed = T)
is_directed(il_net_t1)
```

Plot graphs
```{r}
toa <- diffnet_sw$toa  # pull time of adoption
adopted_at_time_1 <- !is.na(toa) & toa <= 1  # pull nodes that adopted at time 1
sw_nets <- diffnet_to_igraph(diffnet_sw, slices = c(1:10))  #extract network
sw_net_t1 <- sw_nets[[1]]  #extract network at time 1
V(sw_net_t1)$adopted <- adopted_at_time_1  # add adoption to network
sw_net_plot <- ggraph(sw_net_t1) + 
  geom_edge_link(alpha = 0.5) +
  geom_node_point(aes(color = adopted), size = 3) +
  scale_color_manual(values = c("black", "red")) +
  theme_graph()
sw_net_plot

toa <- diffnet_il$toa  # pull time of adoption
adopted_at_time_1 <- !is.na(toa) & toa <= 1  # pull nodes that adopted at time 1
il_nets <- diffnet_to_igraph(diffnet_il, slices=c(1:10))
il_net_t1 <- il_nets[[1]]  # Network at time 1
V(il_net_t1)$adopted <- adopted_at_time_1  # add adoption to network
il_net_plot <- ggraph(il_net_t1) + 
  geom_edge_link(alpha = 0.5) +
  geom_node_point(aes(color = adopted), size = 3) +
  scale_color_manual(values = c("black", "red")) +
  theme_graph()
il_net_plot

nets <- ggarrange(
  sw_net_plot + theme(text = element_text(family = "sans")),
  il_net_plot + theme(text = element_text(family = "sans")),
  ncol = 2
)
nets
```

There are other kinds of random networks that you can use, like scale-free or bernoulli/ER. 
```{r}
set.seed(3)
diffnet_sf <- rdiffnet(
  n = 63,
  t = 10, 
  seed.graph = "scale-free",
  seed.nodes = c(1, 25, 50), # chosen nodes
  seed.p.adopt = .1,
  rewire = F,
  threshold.dist = function(i) 0.25,
  exposure.args = list(normalized = T)
)
diffnet_sf
summary(diffnet_sf)
table(diffnet_sf$toa) # time of adoption
plot_diffnet(diffnet_sf, slices = c(1, 3, 5))
plot_adopters(diffnet_sf, what = "cumadopt", include.legend = FALSE)
plot_adopters(diffnet_sf, what = "adopt") 

diffnet_il # from illustrative graph
cumadopt_sf <- cumulative_adopt_count(diffnet_sf)["prop", ]
cumadopt_il

adopt_data <- data.frame(
  time = rep(1:length(cumadopt_sf), 2),
  adopters = c(cumadopt_sf, cumadopt_il),
  diffusion = rep(c("Diffusion SF", "Diffusion Il"), each = length(cumadopt_sf))
)

ggplot(adopt_data, aes(x = time, y = adopters, color = diffusion)) +
  geom_line(size = 1.2, alpha = 0.5) +
  labs(x = "Time", y = "Proportion of Adopters", 
       title = "Comparison of Simulated vs Real Graph Diffusion") +
  theme_minimal() 
```

Check network attributes
```{r}
## find degree distribution of the two graphs - SF should be higher because of hubs
sf_nets <- diffnet_to_igraph(diffnet_sf, slices=c(1:10))
sf_net_t1 <- sf_nets[[1]]  # Network at time 1

il_nets <- diffnet_to_igraph(diffnet_il, slices=c(1:10))
il_net_t1 <- il_nets[[1]]  # Network at time 1

class(sf_net_t1)
class(il_net_t1)
summary(igraph::degree(sf_net_t1))
summary(igraph::degree(il_net_t1))
```

ER Random graph
```{r}
set.seed(3)
diffnet_er <- rdiffnet(
  n = 63,
  t = 10, 
  seed.graph = "bernoulli",
  seed.nodes = c(1, 25, 50), # chosen nodes
  seed.p.adopt = .1,
  rewire = F,
  threshold.dist = function(i) 0.25,
  exposure.args = list(normalized = T)
)
diffnet_er
summary(diffnet_er)
table(diffnet_sf$toa) # time of adoption
plot_diffnet(diffnet_er, slices = c(1, 3, 5))
plot_adopters(diffnet_er, what = "cumadopt", include.legend = FALSE)
plot_adopters(diffnet_er, what = "adopt")

diffnet_il # from illustrative graph
cumadopt_er <- cumulative_adopt_count(diffnet_er)["prop", ]
cumadopt_il

adopt_data <- data.frame(
  time = rep(1:length(cumadopt_er), 2),
  adopters = c(cumadopt_er, cumadopt_il),
  diffusion = rep(c("Diffusion ER", "Diffusion Real"), each = length(cumadopt_er))
)
ggplot(adopt_data, aes(x = time, y = adopters, color = diffusion)) +
  geom_line(size = 1.2, alpha = 0.5) +
  labs(x = "Time", y = "Proportion of Adopters", 
       title = "Comparison of Simulated vs Real Graph Diffusion") +
  theme_minimal()
```

Check network attributes
```{r}
## find density/clustering of the two graphs - ER should be lower
er_nets <- diffnet_to_igraph(diffnet_er, slices=c(1:10))
er_net_t1 <- er_nets[[1]]  # Network at time 1

il_nets <- diffnet_to_igraph(diffnet_il, slices=c(1:10))
il_net_t1 <- il_nets[[1]]  # Network at time 1

class(er_net_t1)
class(il_net_t1)
transitivity(er_net_t1, type = "global")
transitivity(il_net_t1, type = "global")
transitivity(er_net_t1, type = "average")
transitivity(il_net_t1, type = "average")
edge_density(er_net_t1)
edge_density(il_net_t1)
```

Run a lot of simulations of the diffusion process
```{r}
# rdiffnet_multiple is like rdiffnet, but creates multiple simulations
# running here over the illustrative graph

cores <- detectCores() - 1 #leave 1 free

nsim <- 50 #50 simulations

set.seed(1)
ans_1 <- rdiffnet_multiple(
  R              = nsim, #simulations
  statistic      = function(d) cumulative_adopt_count(d)["prop",], #keep track of the proportion of adopters
  seed.graph     = net_sna_adj,
  t              = 10, #10 time points
  seed.nodes     = "random", #choose random seeds
  seed.p.adopt   = 0.5, #proportion of early adopters
  rewire         = FALSE, #don't rewire slices
  threshold.dist = 1, #set the threshold to 1 (can also run a sample like this: sample(2, n_nodes, TRUE))
  exposure.args  = list(normalized = F),
  ncpus          = cores #run over multiple cores to speed it up
) |> t() #transpose the output

set.seed(1)
ans_2 <- rdiffnet_multiple(
  R              = nsim,
  statistic      = function(d) cumulative_adopt_count(d)["prop",],
  seed.graph     = net_sna_adj,
  t              = 10,
  seed.nodes     = "random",
  seed.p.adopt   = 0.5,
  rewire         = FALSE,
  threshold.dist = 2,
  exposure.args  = list(normalized = F),
  ncpus          = cores
) |> t()

set.seed(1)
ans_3 <- rdiffnet_multiple(
  R              = nsim,
  statistic      = function(d) cumulative_adopt_count(d)["prop",],
  seed.graph     = net_sna_adj,
  t              = 10,
  seed.nodes     = "random",
  seed.p.adopt   = 0.5,
  rewire         = FALSE,
  threshold.dist = 3,
  exposure.args  = list(normalized = F),
  ncpus          = cores
) |> t()
```

Look at the adoption curves for all of the simulations
```{r}
# convert above to dataframes
df1 <- as.data.frame(ans_1)
df2 <- as.data.frame(ans_2)
df3 <- as.data.frame(ans_3)

# mark the threshold value (since that is what I varied)
df1$threshold <- "1"
df2$threshold <- "2"
df3$threshold <- "3"

# make combo dataframe
df_combined <- bind_rows(df1, df2, df3) %>%
  pivot_longer(cols = -threshold, names_to = "time", values_to = "prop")

# Convert Time to numeric
df_combined$time <- as.numeric(df_combined$time)

# df_combined1 <- df_combined %>%
#   dplyr::filter(time == 1) %>%
#   dplyr::group_by(threshold) %>%
#   dplyr::summarize(mean_p = mean(prop)) # check mean at time 1

ggplot(df_combined, aes(x = as.factor(time), y = prop, fill = threshold)) +
  geom_boxplot(alpha = 0.75) +
  scale_fill_manual(values = c("cadetblue1", "cadetblue3", "cadetblue4")) +
  labs(x = "Time", y = "Proportion of Adopters", 
       title = "Adoption over Time by Threshold") +
  theme_minimal() +
  ylim(0, 1)

```

```{r}
V(net)$name
```


```{r}
# Remove KAY from the network
net4 <- igraph::delete_vertices(net, "Kay")

# Visualize the network without KAY
ggraph(net) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "black", fill = "#efd9d3", shape = 21, size = 3) +
  geom_node_text(aes(label = name), repel = TRUE, size = 4, color = "black") +
  theme_graph()
```

```{r}
# Remove KAY from the network
net4 <- igraph::delete_vertices(net, "Kay")

# Visualize the network WITHOUT KAY (using net4, not net)
ggraph(net4) +
  geom_edge_link(color = "black", alpha = 0.3) +
  geom_node_point(color = "black", fill = "#efd9d3", shape = 21, size = 3) +
  geom_node_text(aes(label = ""), repel = TRUE, size = 4, color = "black") +
  theme_graph()
```

```{r}
plot_adopters(diffnet_simple, what = "cumadopt", include.legend = FALSE)
```


```{r}
set.seed(3)

# Create scale-free adjacency matrix
net_matrix <- rgraph_ba(t = 27, m = 2)

# Find central node from matrix
library(igraph)
net_tmp <- graph_from_adjacency_matrix(net_matrix, mode = "undirected")
central_node <- which.max(degree(net_tmp))

# Run diffusion
diffnet_sf <- rdiffnet(
  seed.graph = net_matrix,
  n = 28,
  t = 10, 
  seed.nodes = central_node,
  seed.p.adopt = 0.2,
  rewire = FALSE,
  threshold.dist = function(i) 0.25,
  exposure.args = list(normalized = TRUE)
)

# Verify it worked
summary(diffnet_sf)
plot(diffnet_sf)
```
```{r}
plot_adopters(diffnet_sf, what = "cumadopt", include.legend = FALSE)
```

```{r}
set.seed(3)



# Run diffusion
diffnet_sf <- rdiffnet(
  seed.graph = adj_matrix,
  n = 28,
  t = 20, 
  seed.p.adopt = 0.2,
  rewire = FALSE,
  threshold.dist = function(i) 0.25,
  exposure.args = list(normalized = TRUE)
)

# Verify it worked
summary(diffnet_sf)
plot(diffnet_sf)
```


```{r}
set.seed(3)

# Create the diffusion with all nodes
diffnet_sf <- rdiffnet(
  n = 28,
  t = 20, 
  seed.graph = "scale-free",
  seed.p.adopt = 0.2,  # Set to 1 since we're manually selecting 20%
  rewire = FALSE,
  threshold.dist = function(i) 0.25,
  exposure.args = list(normalized = TRUE)
)

# View the adoption matrix
adoption_matrix <- diffnet_sf$adoption
print(adoption_matrix)

# See which nodes adopted at each time
adopters <- diffnet_sf$cumadopt
print(adopters)

# Summary to verify ~20% adoption
summary(diffnet_sf)

# Visualize adoption over time
plot(diffnet_sf)

```


```{r}
# Get your network as an adjacency matrix
adj_mat <- as.matrix(get.adjacency(un_net, sparse = FALSE))

# Basic model with minimal parameters - FASTER ADOPTION
diffnet_simple <- rdiffnet(
  seed.graph = adj_mat,  # Use seed.graph, not graph
  n = nrow(adj_mat),
  t = 10,
  seed.nodes = which(V(un_net)$name == "Kay"),
  seed.p.adopt = 0.20,
  exposure.args = list(normalized = TRUE)
)

summary(diffnet_simple)
plot(diffnet_simple)

# To make adoption even faster, add a lower threshold
diffnet_simple_fast <- rdiffnet(
  seed.graph = adj_mat,
  n = nrow(adj_mat),
  t = 15,
  seed.nodes = which(V(un_net)$name == "Kay"),
  seed.p.adopt = 0.20,
  threshold.dist = function(i) 0.20,  # Lower threshold = faster adoption
  exposure.args = list(normalized = TRUE)
)

summary(diffnet_simple_fast)
plot(diffnet_simple)
```

```{r}
plot_adopters(diffnet_simple, what = "cumadopt", include.legend = FALSE)
```

